\documentclass{llncs}
\pagestyle{plain}

\usepackage{src/mypreamble}
\include{commands}

\title{Strong Impossibility on Tightly Secure Key Encapsulation and Key Exchange}
%\subtitle{Subtitle}
\titlerunning{Strong Impossibility on Tightly Secure Key Exchange}
\date{\now}
%\author{Authors}
%\institute{Institutes}



\begin{document}

\maketitle

\begin{abstract}
	Authenticated key exchange (AKE) protocols run at a large scale, and their security loss affects their security guarantee and the theoretically sound parameter selection. Using key encapsulation mechanisms (KEMs) is a well-known approach in constructing AKE protocols, for instance, the lattice-based ones. In this paper, we study tightness of KEM-based AKE protocols with a focus on lattice-based constructions.
	
	\quad More precisely, we consider the enhanced chosen-plaintext (ECPA) security of KEM, a notion proposed by Han, Liu, and Gu (ASIACRYPT 2021). We use a combinatorial argument to show that if an adversary involves $2 \lambda$ many users and $11 \lambda p(\lambda)$ ciphertexts, then the security reduction has to lose a linear factor on the number of users $\mu$ in the \emph{standard model}. Hence, its security cannot be tight. In the previous impossibility result of Han et al., it requires the KEM to have polynomially-bounded ranks and it only rules out a class of KEMs based on the Diffie-Hellman assumption. However, our result is more general and does not require polynomially-bounded ranks, and thus it can capture those KEMs based on lattices. Since the ECPA-secure KEM is related to the AKE security, an application of our result is excluding any tightly secure AKE, where the protocol transcripts are independent of the long-term secret keys.
\end{abstract}

%\blankpage

\input{src/introduction}

\input{src/proof_outline}

\input{src/prelims}

\input{src/main_result}

\input{src/applications}

\appendix

\input{src/appendix}

\bibliographystyle{splncs04} % ??????
\bibliography{cryptobib/abbrev3,cryptobib/crypto,refs}

\end{document}
