
\section{Preliminaries}


\begin{definition}[\((1-\delta)\)-correctness of a KEM]\label{def:corr}
  Let \(\KEM = (\Setup, \KG, \Encaps, \Decaps)\) be a KEM
  and let \(\delta : \mathbb{N} \to \mathbb{R}\) be a function of the security parameter.
  Then \KEM is said to have \emph{\((1-\delta)\)-correctness} if
  \begin{equation}
    \prob{\Decaps{}(\sk,c) \ne k : \params \assign \Setup{}(1^{\lambda}), (\sk,\pk) \assign \KG{}(\params), (c,k) \assign \Encaps{}(\pk)} \le \delta (\lambda)
  \end{equation}
\end{definition}

\subsection{Computational assumptions}

When we prove our tightness impossibility results,
we will only be able to rule out tight reductions from a specific class of computational assumptions.
That is, we can only show that a tight reduction to a certain security game \gameG is impossible
if the assumption being reduced from is sufficiently restricted.
This is in some sense an inherent limitation, as we could not rule out a tight reduction to the game \gameG
from \emph{any} computational assumption
(a standard counterexample to this is to use the assumption that the game \gameG is secure.
Clearly there is a tight reduction from this assumption to the game \gameG).
Hence we need the assumption being reduced from to be ``weaker''
than the game \gameG, in a certain sense.

In the impossibility results of \TODO{cite}, the class of computational assumptions
in question are the so-called \emph{non-interactive} assumptions.
These are modeled by experiments in which an adversary receives a challenge \(c\)
and must output a solution \(s\) to the challenge, with no further interaction between the adversary and the experiment.
Following an observation of \TODO{cite}, we will actually slightly expand the class of computational assumptions
from which we can rule out tight reductions, at essentially no cost to the complexity of our proofs.

In \TODO{cite}, it is shown that a tight, simple reduction from the \emph{Strong Diffie-Hellman} assumption
to the weak forward secrecy of a certain class of key exchange protocols cannot exist,
unless the Strong Diffie-Hellman assumption is itself false.
The key point here is that the Strong Diffie-Hellman game is interactive,
and hence does not fit into the class of non-interactive assumptions considered in e.g \TODO{cite}.
Nevertheless \TODO{cite} are able to apply a similar meta-reduction strategy
to the one pioneered in \TODO{cite} to prove their impossibility result.
We observe that the Strong Diffie-Hellman game satisfies the following two criteria,
which allow the proof of \TODO{cite} to go through.
The first is that the interaction in the Strong Diffie-Hellman game is in some sense stateless.
More precisely, the Strong Diffie-Hellman oracle computes its answer to a query
in a way that is independent of the content of any previous queries.
Second, the ``winning condition'' in the Strong Diffie-Hellman game is essentially independent of
the queries made to the Strong Diffie-Hellman oracle.
\TODO{explain why this is the case.}

We can define a class of interactive computational assumptions in which the above two criteria are met.
We will call such an assumption a \emph{simple computational assumption}.
\TODO{say something more.}

\begin{definition}[Simple computational assumption]
  A simple computational assumption is a tuple \((\Init,\Respond,\Win,\epsilon)\),
  where \(\epsilon : \N \to \R\) is a function,
  \(\Init\) is a probabilistic algorithm
  and \(\Respond\) and \(\Win\) are deterministic algorithms.
  For a given simple computational assumption \((\Init,\Respond,\Win,\epsilon)\),
  we define an experiment \(\Simple\) as follows:

  \begin{pchstack}[center,space=0.5cm]
    \proc{Game \Simple{}$(\advA,\lambda)$}{
      (\state_{\Simple}, c) \assign \Init(1^{\lambda}).\\
      s \assign \advA^{\oracle}(c).\\
      b' \assign \Win(\state_{\Simple},s).\\
      \pcreturn b'.
    }
    \proc{Oracle \oracle(m)}{
      \pcreturn \Respond(\state_{\Simple},m).
    }
  \end{pchstack}

  Here, \Win{} defines the ``winning condition'' in the game.
  Notice that \Win{} depends only on the initial state \(\state_{\Simple}\)
  of \Simple and the challenge solution \(s\) output by \advA
  (in particular, it does not depend on the queries made by \advA
  to \oracle during the game).
  Also, whenever \advA queries the oracle \oracle,
  the response is computed deterministically as \(\Respond(\state_{\Simple},m)\).
  The advantage of \advA{} against \Simple is given by
  \TODO{advantage notation.}
  \begin{equation}
    \abs[\big]{\prob{\Simple{}(\advA,\lambda) \implies 1} - \epsilon(\lambda)}.
  \end{equation}
  \TODO{say something about epsilon.}
\end{definition}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:
